Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-26 paper/paper.Rmd
discernables -> detectability

Conceptually, LLTO applies zero-distance buffering in both space and time: The buffer zones consist of all observations whose distance to the test sample in either space or time equals zero.
In the mathematical sense, however, this buffering is not based on a valid metric (or distance function) in three-dimensional space (2D + time) as neither the identity of discernables nor the triangle inequality are satisfied by the underlying combined 'distance' measure.
Also note that LLTO does not 'combine' LTO with LLO, as neither of these applies a buffer zone.

>>>>

Conceptually, LLTO applies zero-distance buffering in both space and time: The buffer zones consist of all observations whose distance to the test sample in either space or time equals zero.
In the mathematical sense, however, this buffering is not based on a valid metric (or distance function) in three-dimensional space (2D + time) as neither the identity of detectability nor the triangle inequality are satisfied by the underlying combined 'distance' measure.
Also note that LLTO does not 'combine' LTO with LLO, as neither of these applies a buffer zone.
